Towards ....

### 2015-03-25 paper/nodalida2015.tex
fix formatting of bibtex

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\usepackage{cite}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

@@

Application of logic to POS tagging or shallow parsing isn't new;
\cite{lager98, lager_nivre01} present constraint rules as 
a disjunctive logic program.

Our implementation is inspired by this approach,
but unlike Lager's our implementation tries to emulate the CG
formalism in behaviour and features offered.
% What we do better: implement something that takes existing CG rules and applies them to text, trying to mimic/outperform current CG implementations.

>>>>

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\usepackage{cite}
\usepackage{authordate1-4}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

Our implementation is inspired by approaches like \cite{lager98,lager_nivre01},
but we try to emulate the CG formalism more closely, and use the same rule files.

@@

Application of logic to POS tagging or shallow parsing isn't new;
\cite{lager98,lager_nivre01} present constraint rules as 
a disjunctive logic program.

\cite{lindberg_eineborg98ilp,asfrent14}

% What we do better: implement something that takes existing CG rules and applies them to text, trying to mimic/outperform current CG implementations.
